Proposed Solution

### 2016-11-10 Ennan-Proposal/motivation.tex
stuff

The goal of this proposal is to develop a fully {\bf {automated 
verification  framework for general software configurations}}. We plan to
overcome the above obstacles by first automatically inferring a
specification for configuration files. It is unrealistic to expect the 
users to write a specifications for configuration files on their own. 
This process can easily lead to incomplete or even contradictory 
specifications.  Instead, we will learn specification from 
a large sample of 
configuration files. We start a learning process that takes as input this 
sample. The process will be language-agnostic and should work for any kind 
of configuration files,  but all of the files in the sample need to be of 
the same kind (such as MySQL or 
HTTPD configuration files). From that sample, we will learn an abundant set of rules 
specifying various properties that hold on the given sample. The rules, in general, 
specify which properties variables in configuration files need to satisfy. One can see this learning process as 
a way of deriving  a specification for configuration files. With these  rules we can efficiently check 
the correctness of the configuration files of interest and detect 
potential errors. Errors are reported if the configuration file does not 
adhere to a specification.

@@

Building such an automatic verification framework for
configuration files requires addressing several challenges. 
First, in the process of inferring a specification, we have to 
analyze mainly with an untyped, unstructured sequence of assignments.
Thus, we need to develop a suitable language model. We do that by 
``guessing'' a type of variables and then deriving formulas that
describe relationships between these variables. However, the
type of a variable cannot always be fully determined 
from a single value. 
For example, an entry {\tt something = 1} assigns 
\ruzica{here, something is 1 which is int, but it is actually a Boolean}
\ruzica{more story here}
Some existing type inference 
work would report this is an error, because {\tt temp\_dir} should be assigned
an integer~\cite{zhang14encore}. We address this problem by introducing the concept of
{\emph{probabilistic types}}.
Rather than assigning only one variable to a single type, 
we assign several types over a probability distribution. 
Using probabilistic types,
we aim to generate a more accurate language model,
thus significantly improving our verification capabilities.

>>>>

The goal of this proposal is to develop a fully {\bf {automated 
verification  framework for general software configurations}}. We plan to
overcome the above obstacles by first automatically inferring a
specification for configuration files. It is unrealistic to expect the 
users to write an entire specifications for configuration files on their own. 
This process can easily lead to incomplete or even contradictory 
specifications. Instead, we will learn specification from 
a large sample of 
configuration files. A learning process will take as input this 
sample. The process will be language-agnostic and should work for any kind 
of configuration files,  but all of the files in the sample need to be of 
the same kind (such as MySQL or 
HTTPD configuration files). From that sample, we will learn an abundant set of rules 
specifying various properties that hold on the given sample. The rules, in general, 
specify which properties variables in configuration files need to satisfy. One can see this learning process as 
a way of deriving  a specification for configuration files. With these  rules we can efficiently check 
the correctness of the configuration files of interest and detect 
potential errors. Errors are reported if the configuration file does not 
adhere to a specification.

@@

Building such an automatic verification framework for
configuration files requires addressing several challenges. 
First, in the process of inferring a specification, we have to 
analyze mainly with an untyped, unstructured sequence of assignments.
Thus, we need to develop a suitable language model. We do that by 
``guessing'' a type of variables and then deriving formulas that
describe relationships between these variables. However, the
type of a variable cannot always be fully determined 
from a single value. 
An entry {\tt general\_log = 1} assigns an integer to the 
variable {\tt general\_log}. However, 1 here is a Boolean variable,
which denotes that there will be a general log file.
Another example, which shows how this can easily lead to an error, is 
that sometimes a configuration files 
contain the following entry {\tt general\_log = /var/log/mysql/mysql.log}. This will cause    
\ruzica{what will actually happen in this case}
Some existing type inference 
work would report this is an error, because {\tt temp\_dir} should be assigned
an integer~\cite{zhang14encore}. We address this problem by introducing the concept of
{\emph{probabilistic types}}.
Rather than assigning only one variable to a single type, 
we assign several types over a probability distribution. 
Using probabilistic types,
we aim to generate a more accurate language model,
thus significantly improving our verification capabilities.
